---
title: "Some data from NOAA"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source: embed
    theme: simplex
    navbar: 
    - {title: "Home", href: index.html}
    - {title: "CV", href: about.html}
    - {icon: fa-envelope, href: mailto:<jae2186@cumc.columbia.edu>}
    - {icon: fa-github, href: http://github.com/jestrada4919/}
    - {icon: fa-linkedin, href: https://www.linkedin.com/in/jenniferaestrada/}   
---
<b>For this exercise in setting up a dashboard, I have pulled data  from the Daily Global Historical Climatology Network (GHCN-DAILY) provided by the National Oceanic and Atmospheric Administration (NOAA). I have chosen 3 locations of interest to compare temperature and precipitation data; these locations are:</b>

* Auckland, New Zealand - a place I hope to visit someday,
* Tegucigalpa, Honduras - a place I have visited when seeing family, and 
* University Park, PA - a place I am familiar with having attended graduate school there.

<b>Reference</b>: Menne, M.J., I. Durre, B. Korzeniewski, S. McNeal, K. Thomas, X. Yin, S. Anthony, R. Ray, R.S. Vose, B.E.Gleason, and T.G. Houston, 2012: Global Historical Climatology Network-Daily (GHCN-Daily), Version 3. [indicate subset used following decimal, e.g. Version 3.12]. NOAA National Climatic Data Center. http://doi.org/10.7289/V5D21VHZ [accessed Nov. 6, 2021].

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(rnoaa)
```

```{r data_setup}

weather_df = 
  rnoaa::meteo_pull_monitors(
    c("NZM00093110", "HO000078720", "USC00368449"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2015-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      NZM00093110 = "Auckland, New Zealand", 
      HO000078720 = "Tegucigalpa, Honduras",
      USC00368449 = "University Park, PA"),
    tmin = tmin / 10,
    tmax = tmax / 10,
    prcp = prcp *10,
    month = lubridate::floor_date(date, unit = "month"),
    year = lubridate::floor_date(date, unit = "year")) %>%
  select(name, id, everything()) %>% 
  drop_na(prcp, tmax, tmin)

```
 

Column {data-width=650}
-----------------------------------------------------------------------

### (A) How does maximum temperature change throughout the year in these 3 locations?

```{r charta}
weather_df %>% 
  mutate(text_label = str_c("Precipitation: ", prcp, " mm")) %>% 
  plot_ly(x = ~date, y = ~tmax, color = ~name, alpha = 0.5,
          type = "scatter", mode = "lines", text = ~text_label, colors = "viridis"
          ) %>% 
  layout(title = 'Maximum Temperature by Location (2015-2017)', 
         xaxis = list(title = 'Date'), 
         yaxis = list(title = 'Maximum Temperature (˚C)'), 
         legend = list(title = list(text = '<b> Location </b>')))


```

Column {data-width=350}
-----------------------------------------------------------------------

### (B) Looking at data from a single year (specifically 2015), what are the distributions for monthly maximum temperature for each of these locations?

```{r chartb}
weather_df %>% 
  group_by(month, name) %>% 
  filter(year == "2015-01-01") %>% 
  plot_ly(
    x = ~month, y = ~tmax, color = ~name, 
    type = "box", colors = "viridis") %>% 
  layout(title = 'Maxu', 
         xaxis = list(title = 'Date'), 
         yaxis = list(title = 'Maximum Temperature'), 
         legend = list(title = list(text = '<b> Location </b>')))



```

### (C) And in 2015 how many days did these locations experience precipitation (of any kind) each month?

```{r chartc}
weather_df %>% 
  mutate(precipdays = ifelse(prcp > 0, "yes", "no")) %>% 
  filter(precipdays == "yes", year == "2015-01-01") %>% 
  group_by(month, name) %>% 
  count(precipdays) %>% 
  plot_ly(
    x = ~month, y = ~n, color = ~name, 
    type = "bar", colors = "viridis") %>% 
  layout(title = 'Annual Precipitation Days', 
         xaxis = list(title = 'Date'), 
         yaxis = list(title = 'Number of precipiation days'), 
         legend = list(title = list(text = '<b> Location </b>')))

```

